---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# ari_test

The goal of `ari_test` is to provide a simple example for using [`ari`](https://github.com/seankross/ari) on http://shinyapps.io.  In order to use `aws.polly`, you need to upload credentials to the repo.   
The app is hosted on https://jhubiostatistics.shinyapps.io/ari_test/ currently.  


Currently, you must use `video_codec = NULL` and `ffmpeg_opts = "-strict -2"` for it to work due to the `ffmpeg` installation on that platform.  

The code only works with the `muschellij2/ari` version of `ari` (https://github.com/muschellij2/ari) which can be installed by:

```r
devtools::install_github("muschellij2/ari")
```

## Devtools Info

Here is the setup for running and publishing this app:

```{r}
library(ari)
library(animation)
library(tuneR)
library(shiny)
devtools::session_info()
```
